---
title: "Quatatative Management 1"
author: "Sumit Dutt Mishra"
date: "9/11/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Q1: Data Source
Our dataset **Medals** has been extracted from **KAGGLE** , is a collection of database and datasets used by Machine Learning community for the analysis of Machine Learning algorithms

###Q2: Importing Medal Dataset to R Studio

```{r }
setwd("C:/Users/User/Downloads/archive (2)")
Medals<- read.csv("C:/Users/User/Downloads/archive (2)/Tokyo Medals 2021.csv")
head(Medals)
```

###Q3: Descriptive Analysis of Medals Dataset
Inspecting Dataset

```{r message=FALSE}
summary(Medals)

####Arithmetic Mean :AM of a set of observation is defined as a sum divided by number of observations
```{r }
####Mean of overall Medals
mean(Medals$Total)

```
**Median :** is the the middle value of the observation
####Rank of team with bronze
```{r }
#### Median of Bronze
median(sort(Medals$Bronze))
```

**Mode:** refers to the value which occurs to the maximum frequency
####Which team got maximum Gold

```{r }
sort(table(Medals$Gold),decreasing = TRUE)
```
###Q4: Transformation
####Applying log transformation on Silver Column
```{r }
Silver_Medals<- log10(Medals$Silver)
## Displaying first 10 values
Silver_Medals[1:10]

```
###Q5: Visualisation
**Histogram Plot**

```{r message=FALSE, warning=FALSE}
library(ggplot2)
ggplot(Medals,aes(x=Gold.Medal))+ geom_histogram()+ggtitle('Histogram Graph')

```
**Scatter Plot

```{r }
ggplot(Medals,aes(x=Total, y= Rank.By.Total))+geom_point()+ggtitle('Scatter Plot')
```

